\textbf{\huge{Arcane Trickster}}

\textbf{Hit Die}: d4

\textbf{Skills}: Appraise (Int), Balance (Dex), Bluff (Cha), Climb (Str), Concentration (Con), Craft (Int), Decipher Script (Int), Diplomacy (Cha), Disable Device (Int), Disguise (Cha), Escape Artist (Dex), Forgery (Int), Gather Information (Cha), Handle Animal (Cha), Heal (Wis), Hide (Dex), Intimidate (Cha), Jump (Str), Knowledge (all skills, taken individually) (Int), Listen (Wis), Move Silently (Dex), Open Lock (Dex), Perform (Cha), Profession (Wis), Ride (Dex), Search (Int), Sense Motive (Wis), Sleight of Hand (Dex), Speak Language (None), Spellcraft (Int), Spot (Wis), Survival (Wis), Swim (Str), Tumble (Dex), Use Magic Device (Cha), Use Rope (Dex)

\textbf{Skills/Level}: 2 + Int modifier

\textbf{\large{Requirements}}

To qualify to become an arcane trickster, a character must fulfill all of the following criteria.

\textbf{Skills}: Spellcraft 6 ranks

\textbf{Spells}: Able to cast 1st level arcane spells.

\textbf{Special}: Sneak attack +1d6

\begin{center}
\begin{adjustwidth}{-4cm}{}
\begin{small}
\begin{tabular}{| c | c | c | c | c | c | c |}
\hline
LVL &BAB &F &R &W &Special &Spellcasting \\
\hline
1 &0 &0 &2 &2 &Ranged legerdemain &+1 level of existing spellcasting class \\
2 &1 &0 &3 &3 &Sneak attack +1d6 &+1 level of existing spellcasting class \\
3 &1 &1 &3 &3 &Impromptu sneak attack &+1 level of existing spellcasting class \\
\hline
\end{tabular}
\end{small}
\end{adjustwidth}
\end{center}

\textbf{Spellcasting}: When an arcane trickster advances in level, the character gains new spells per day as if he had also gained a level in a spellcasting class he belonged to before adding the prestige class. He does not, however, gain any other benefit a character of that class would have gained, except for an increased effective level of spellcasting. If a character had more than one spellcasting class before becoming a loremaster, he must decide to which class he adds the new level for purposes of determining spells per day.


\textbf{Ranged Legerdemain}: An arcane trickster can perform the following class skills at a range of 30 feet: Disable Device, Open Lock, or Sleight of Hand. Working at a distance increases the normal skill check DC by 5, and an arcane trickster cannot take 10 on this check. Any object to be manipulated must weigh 5 pounds or less.

\textbf{Sneak Attack}: This is exactly like the rogue ability of the same name. If the arcane trickster gets a sneak attack bonus from another source the bonuses on damage stack.

\textbf{Impromptu Sneak Attack}: Once per day a third level arcane trickster can declare one melee or ranged attack he makes to be a sneak attack (the target can be no more than 30 feet distant if the impromptu sneak attack is a ranged attack). The target of an impromptu sneak attack loses any Dexterity bonus to AC, but only against that attack. The power can be used against any target, but creatures that are not subject to critical hits take no extra damage (though they still lose any Dexterity bonus to AC against the attack).