\textbf{\huge{Eldritch Knight}}

\textbf{Hit Die}: d6

\textbf{Skills}: Concentration (Con), Craft (Int), Decipher Script (Int), Jump (Str), Knowledge (arcana) (Int), Knowledge (nobility and royalty) (Int), Ride (Dex), Sense Motive (Wis), Spellcraft (Int), Swim (Str)

\textbf{Skills/Level}: 2 + Int modifier

\textbf{\large{Requirements}}

To qualify to become an eldritch knight, a character must be able to cast 1st level arcane spells.

\begin{center}
\begin{adjustwidth}{-4cm}{}
\begin{small}
\begin{tabular}{| c | c | c | c | c | c | c |}
\hline
LVL &BAB &F &R &W &Special &Spellcasting \\
\hline
1 &1 &2 &0 &2 &Armored caster, martial weapon proficiency &- \\
2 &2 &3 &0 &3 &Armor proficiency (Light) &+1 level of existing spellcasting class \\
3 &3 &3 &1 &3 &Armor proficiency (Medium) &+1 level of existing spellcasting class \\
4 &4 &4 &1 &4 &Armor proficiency (Heavy) &+1 level of existing spellcasting class \\
5 &5 &4 &1 &4 & &+1 level of existing spellcasting class \\
\hline
\end{tabular}
\end{small}
\end{adjustwidth}
\end{center}

\textbf{Weapon and Armor Proficiency}: Eldritch knights gain no proficiency with any weapon or armor.

\textbf{Spells per Day}: When an eldritch knight reaches levels 2 through 5, the character gains new spells per day as if he had also gained a level in a spellcasting class he belonged to before adding the prestige class. He does not, however, gain any other benefit a character of that class would have gained, except for an increased effective level of spellcasting. If a character had more than one spellcasting class before becoming an eldritch knight, he must decide to which class he adds the new level for purposes of determining spells per day.

\textbf{Armored Caster}: A 1st level eldritch knight gains the ability to reduce her arcane spell failure chance by 20%. At each subsequent eldritch knight level this ability increases by 5%, up to 40% at 5th level.

\textbf{Martial Weapon Proficiency}: A 1st level eldritch knight gains the feat Martial Weapon Proficiency.

\textbf{Armor Proficiency (Light)}: A 2nd level eldritch knight gains the feat Armor Proficiency (Light)

\textbf{Armor Proficiency (Medium)}: A 3rd level eldritch knight gains the feat Armor Proficiency (Medium).

\textbf{Armor Proficiency (Heavy)}: A 3rd level eldritch knight gains the feat Armor Proficiency (Heavy).