\textbf{\huge{Thaumaturgist}}

\textbf{Hit Die}: d4

\textbf{Skills}: Concentration (Con), Craft (Int), Diplomacy (Cha), Knowledge (religion) (Int), Knowledge (the planes) (Int), Profession (Wis), Sense Motive (Wis), Speak Language (None), Spellcraft (Int)

\textbf{Skills/Level}: 2 + Int modifier

\textbf{\large{Requirements}}

To qualify to become a thaumaturgist, a character must be able to cast 1st level divine or arcane spells and have taken the feat Spell Focus (conjuration).

\begin{center}
\begin{adjustwidth}{-4cm}{}
\begin{small}
\begin{tabular}{| c | c | c | c | c | c | c |}
\hline
LVL &BAB &F &R &W &Special &Spellcasting \\
\hline
1 &0 &0 &0 &2 &Augment summoning &+1 level of existing spellcasting class \\
2 &1 &0 &0 &3 &Extended summoning &+1 level of existing spellcasting class \\
3 &1 &1 &1 &3 & &+1 level of existing spellcasting class \\
4 &2 &1 &1 &4 &Contingent conjuration &+1 level of existing spellcasting class \\
5 &2 &1 &1 &4 &Planar cohort &- \\
\hline
\end{tabular}
\end{small}
\end{adjustwidth}
\end{center}

\textbf{Weapon and Armor Proficiency}: Thaumaturgists gain no proficiency with any weapon or armor.

\textbf{Spells Per Day}: When a thaumaturgist gains any level besides 1st, the character gains new spells per day as if he had also gained a level in whatever spellcasting class he belonged to before he added the prestige class. He does not, however, gain any other benefit a character of that class would have gained.

If a character had more than one spellcasting class before he became a thaumaturgist, he must decide to which class he adds each level of thaumaturgist for the purpose of determining spells per day.

\textbf{Augment Summoning}: At 1st level, a thaumaturgist gains the Augment Summoning feat.

\textbf{Extended Summoning}: At 2nd level and higher, all spells from the summoning subschool that the thaumaturgist casts have their durations doubled, as if the Extend Spell feat had been applied to them. The levels of the summoning spells don’t change, however. This ability stacks with the effect of the Extend Spell feat, which does change the spell’s level.

\textbf{Contingent Conjuration}: A 4th-level thaumaturgist can prepare a summoning or calling spell ahead of time to be triggered by some other event. This functions as described for the contingency spell, including having the thaumaturgist cast the summoning or calling spell beforehand. The spell is cast instantly when the trigger event occurs.

The conditions needed to bring the spell into effect must be clear, although they can be general. If complicated or convoluted condition as are prescribed, the contingent conjuration may fail when triggered. The conjuration spell occurs based solely on the stated conditions, regardless of whether the thaumaturgist wants it to, although most conjurations can be dismissed normally. A thaumaturgist can have only one contingent conjuration active at a time.

\textbf{Planar Cohort}: A 5th-level thaumaturgist can call on an elemental or outsider of 6 HD or less to act as his cohort. The called creature serves loyally and well as long as the thaumaturgist continues to advance a cause important to the creature.

To call a planar cohort, the thaumaturgist must perform a one hour ritual and provide an offering of 10gp * the HD of the creature. Should the planar cohort die, another can be summoned by repeating this ritual and providing another offering. If the cohort is dismissed (dismissal requires a free action) another can be summoned again with the ritual, this time no offering is necessary.