\textbf{\huge{Psychic Warrior}}

\textbf{Hit Die}: d8

\textbf{Skills}: Autohypnosis (Wis), Climb (Str), Concentration (Con), Craft (Int), Jump (Str), Knowledge (psionics) (Int), Profession (Wis), Ride (Dex), Search (Int), Swim (Str)

\textbf{Skills/Level}: 2 + Int modifier

\begin{center}
\begin{adjustwidth}{-4cm}{}
\begin{small}
\begin{tabular}{| c | c | c | c | c | c | c | c | c |}
\hline
LVL &BAB &F &R &W &Special &Power Points/Day &Powers Known &Maximum Power Level Known \\
\hline
1 &1 &2 &0 &2 &Bonus feat &2 &1 &1st \\
2 &2 &3 &0 &3 & &6 &2 &1st \\
3 &3 &3 &1 &3 &Bonus feat &10 &3 &1st \\
4 &4 &4 &1 &4 & &15 &4 &2nd \\
5 &5 &4 &1 &4 &Bonus feat &19 &5 &2nd \\
6 &6/1 &5 &2 &5 &Bonus feat &26 &6 &2nd \\
\hline
\end{tabular}
\end{small}
\end{adjustwidth}
\end{center}

\textbf{Weapon and Armor Proficiency}: Psychic warriors are proficient with all simple and martial weapons, with all types of armor (heavy, medium, and light), and with shields (except tower shields).

\textbf{Power Points/Day}: A psychic warrior’s ability to manifest powers is limited by the power points he has available. His base daily allotment of power points is given on the table above. In addition, he receives bonus power points per day if he has a high Wisdom score. His race may also provide bonus power points per day, as may certain feats and items. A 1st-level psychic warrior gains no power points for his class level, but he gains bonus power points (if he is entitled to any), and can manifest the single power he knows with those power points.

\textbf{Powers Known}: A psychic warrior begins play knowing one psychic warrior power of your choice. Each time he achieves a new level, he unlocks the knowledge of a new power.

Choose the powers known from the psychic warrior power list. A psychic warrior can manifest any power that has a power point cost equal to or lower than his manifester level.

The total number of powers a psychic warrior can manifest in a day is limited only by his daily power points.

A psychic warrior simply knows his powers; they are ingrained in his mind. He does not need to prepare them (in the way that some spellcasters prepare their spells), though he must get a good night’s sleep each day to regain all his spent power points.

The Difficulty Class for saving throws against psychic warrior powers is 10 + the power’s level + the psychic warrior’s Wisdom modifier.

\textbf{Maximum Power Level Known}: A psychic warrior begins play with the ability to learn 1st-level powers. As he attains higher levels, he may gain the ability to master more complex powers.

To learn or manifest a power, a psychic warrior must have a Wisdom score of at least 10 + the power’s level.

\textbf{Bonus Feats}: At 1st level, a psychic warrior gets a bonus combat-oriented feat in addition to the feat that any 1st level character gets and the bonus feat granted to a human character. The psychic warrior gains an additional bonus feat at 3rd, 5th, and 6th level. These bonus feats must be drawn from the feats noted as fighter bonus feats or psionic feats. The psychic warrior must still meet all prerequisites for the bonus feat, including ability score and base attack bonus minimums as well as class requirements. A psychic warrior cannot choose feats that specifically require levels in the fighter class unless he is a multiclass character with the requisite levels in the fighter class.

These bonus feats are in addition to the feats that a character of any class gains every three levels. A psychic warrior is not limited to fighter bonus feats and psionic feats when choosing these other feats.