\textbf{\huge{Wilder}}

\textbf{Hit Die}: d6

\textbf{Skills}: Autohypnosis (Wis), Balance (Dex), Bluff (Cha), Climb (Str), Concentration (Con), Craft (Int), Escape Artist (Dex), Intimidate (Cha), Jump (Str), Knowledge (psionics) (Int), Listen (Wis), Profession (Wis), Psicraft (Int), Sense Motive (Wis), Spot (Wis), Swim (Str), Tumble (Dex)

\textbf{Skills/Level}: 4 + Int modifier

\begin{center}
\begin{adjustwidth}{-4cm}{}
\begin{small}
\begin{tabular}{| c | c | c | c | c | c | c | c | c |}
\hline
LVL &BAB &F &R &W &Special &Power Points/Day &Powers Known &Maximum Power Level Known \\
\hline
1 &0 &0 &0 &2 &\makecell{Wild surge +1, psychic enervation,\\ psicrystal affinity, discipline} &4 &3 &1st \\
2 &1 &0 &0 &3 &Elude touch &11 &3 &1st \\
3 &2 &1 &1 &3 &Wild surge +2 &18 &3 &1st \\
4 &3 &1 &1 &4 &Surging euphoria &27 &4 &2nd \\
5 &3 &1 &1 &4 &Bonus feat &37 &4 &2nd \\
6 &4 &2 &2 &5 &Wild surge +3 &50 &5 &2nd \\
\hline
\end{tabular}
\end{small}
\end{adjustwidth}
\end{center}

\textbf{Weapon and Armor Proficiency}: Wilders are proficient with all simple weapons, with light armor, and with shields (except tower shields).

\textbf{Power Points/Day}: A wilder’s ability to manifest powers is limited by the power points she has available. Her base daily allotment of power points is given on table above. In addition, she receives bonus power points per day if she has a high Charisma score. Her race may also provide bonus power points per day, as may certain feats and items.

\textbf{Powers Known}: A wilder begins play knowing one wilder power of your choice. At every even-numbered class level after 1st, she unlocks the knowledge of new powers.

Choose the powers known from the wilder power list. A wilder can manifest any power that has a power point cost equal to or lower than her manifester level.

The total number of powers a wilder can manifest in a day is limited only by her daily power points.

A wilder simply knows her powers; they are ingrained in her mind. She does not need to prepare them (in the way that some spellcasters prepare their spells), though she must get a good night’s sleep each day to regain all her spent power points.

The Difficulty Class for saving throws against wilder powers is 10 + the power’s level + the wilder’s Charisma modifier.

\textbf{Maximum Power Level Known}: A wilder begins play with the ability to learn 1st-level powers. As she attains higher levels, she may gain the ability to master more complex powers.

To learn or manifest a power, a wilder must have a Charisma score of at least 10 + the power’s level.

\textbf{Wild Surge}: A wilder can let her passion and emotion rise to the surface in a wild surge when she manifests a power. During a wild surge, a wilder gains phenomenal psionic strength, but may harm herself by the reckless use of her power (see Psychic Enervation, below).

A wilder can choose to invoke a wild surge whenever she manifests a power. When she does so, she gains +1 to her manifester level with that manifestation of the power. The manifester level boost gives her the ability to augment her powers to a higher degree than she otherwise could; however, she pays no extra power point for this wild surge. Instead, the additional 1 power point that would normally be required to augment the power is effectively supplied by the wild surge.

Level-dependent power effects are also improved, depending on the power a wilder manifests with her wild surge.

This improvement in manifester level does not grant her any other benefits (psicrystal abilities do not advance, she does not gain higher-level class abilities, and so on).

She cannot use the Overchannel psionic feat and invoke her wild surge at the same time.

At 3rd level, a wilder can choose to boost her manifester level by two instead of one, and at 6th level she can boost her manifester level by up to three.

In all cases, the wild surge effectively pays the extra power point cost that is normally required to augment the power; only the unaugmented power point cost is subtracted from the wilder’s power point reserve.

\textbf{Psychic Enervation}: Pushing oneself by invoking a wild surge is dangerous. Immediately following each wild surge, a wilder may be overcome by the strain of her effort. The chance of suffering psychic enervation is equal to 5\% per manifester level added with the wild surge.

A wilder who is overcome by psychic enervation is dazed until the end of her next turn.

\textbf{Psicrystal Affinity}: A 1st level wilder gains the feat Psicrystal Affinity. Allowing them to gain a psicrystal.

\textbf{Discipline}: Every wilder must decide at 1st level which psionic discipline he will specialize in. Choosing a discipline provides a wilder with access to the powers restricted to that discipline. However, choosing a discipline also means that the wilder cannot learn powers that are restricted to other disciplines. He can’t even use such powers by employing psionic items.

Unlike a psion, a wilder's selection of class skills is not affected by the discipline he chooses.

\textbf{Elude Touch}: Starting at 2nd level, a wilder’s intuition supersedes her intellect, alerting her to danger from attacks (including touch attacks). She gains a dodge bonus to Armor Class against all attacks equal to her Charisma bonus.

\textbf{Surging Euphoria}: Starting at 4th level, when a wilder uses her wild surge ability, she gains a +1 morale bonus on attack rolls, damage rolls, and saving throws for a number of rounds equal to the intensity of her wild surge.

If a wilder is overcome by psychic enervation following her wild surge, she does not gain the morale bonus for this use of her wild surge ability.

\textbf{Bonus Feat}: A wilder gains a bonus feat at 5th level. This feat must be a psionic feat, a metapsionic feat, or a psionic item creation feat.