\textbf{\huge{Barbarian}}

\textbf{Hit Die}: d12

\textbf{Skills}: Balance (Dex), Climb (Str), Craft (Int), Handle Animal (Cha), Intimidate (Cha), Jump (Str), Listen (Wis), Move Silently (Dex), Ride (Dex), Survival (Wis), Swim (Str), Tumble (Dex)

\textbf{Skills/Level}: 4 + Int modifier

\begin{center}
\begin{adjustwidth}{-4cm}{}
\begin{small}
\begin{tabular}{| c | c | c | c | c | c |}
\hline
LVL &BAB &F &R &W &Special \\
\hline
1 &1 &2 &0 &0 &Fast Movement, Illiteracy, Rage, Power Attack \\
2 &2 &3 &0 &0 &Skirmish +1d6 \\
3 &3 &3 &1 &1 &Damage Reduction 1/-, endurance \\
4 &4 &4 &1 &1 &Greater Fast Movement, Improved Healing \\
5 &5 &4 &1 &1 &Unshakeable \\
6 &6/1 &5 &2 &2 &Damage Reduction 2/-, Greater Improved Healing \\
\hline
\end{tabular}
\end{small}
\end{adjustwidth}
\end{center}

\textbf{Weapon and Armor Proficiency}: A barbarian is proficient with all simple and martial weapons, light armor, medium armor, and shields (except tower shields).

\textbf{Fast Movement(Ex)}: A barbarian's land speed is faster than the norm for his race by +10 ft. This benefit applies only when he is wearing no armor, light armor, or medium armor and not carrying a heavy load. Apply this bonus before modifying the barbarian's speed because of any load carried or armor.

\textbf{Illiteracy}: Barbarians are the only characters who do not automatically know how to read and write. A barbarian may spend 2 skill points to gain the ability to read and write all languages he is able to speak. Any other character who gains a barbarian level does not lose the literacy he or she already had.

\textbf{Rage(Ex)}: Once per day per two class levels a barbarian can enter rage. In a rage, a barbarian temporarily gains +4 Strength, +4 Constitution, +2 morale bonus on Will saves, +1 to their damage reduction, regeneration 1, and an additional +10 to their land speed, but he takes a -2 penalty to Armor Class. Rage lasts for a number of rounds equal to 3 + the barbarian's new Constitution modifier. A barbarian may prematurely end his rage, additionally if his rage would end he may use a free action to immediately transition into another rage.

Because of regeneration, damage a barbarian takes while raging is treated as nonlethal damage, and healed at a rate of 1 hit point per round. Damage taken before entering a rage is treated normally, and any nonlethal damage remaining when a barbarian exits rage is converted to lethal damage.

While raging, a barbarian cannot use any Charisma, Dexterity, or Intelligence based skills (except for Balance, Escape Artist, Intimidate, and Ride), the Concentration skill, or any abilities that require patience or concentration, nor can he cast spells or activate magic items that require a command word, a spell trigger (such as a wand), or spell completion (such as a scroll) to function.

\textbf{Power Attack}: At 1st level a barbarian gains the feat power attack, if the barbarian already has this feat they can instead select a different feat for which they meet the prerequisites.

\textbf{Damage Reduction}: At 3rd level a barbarian gains Damage Reduction. Substract 1 from damage the barbarian takes each time he is dealt damage from a weapon or a natural attack. At 6th level this reduction increases to 2.

\textbf{Endurance}: A barbarian gains endurance as a bonus feat at 3rd level. If they already have this feat they may select another feat for which they meet the prerequisites. 

\textbf{Skirmish}: A 2nd level barbarian deals an extra 1d6 damage on the first attack she makes during any turn in which she moves at least 10 feet away from where she was at the start of her turn. 

\textbf{Greater Fast Movement}: Add +10 to land speed, this stacks with the bonus from fast movement.

\textbf{Improved Healing}: A 4th level barbarian gains an enhancement to their natural healing abilities. Every time a barbarian rests they recover an additional hit point per hit die. 

\textbf{Unshakeable}: A 5th level barbarian who is reduced to between -1 and -9 hit points automatically becomes stable and is not disabled (they are not limited to a single move or standard action each round). 

\textbf{Greater Improved Healing}: A 6th level barbarian's healing improves even further, letting them recover 1 hitpoint for every 60 minutes spent out of combat. 