\textbf{\huge{Horizon Walker}}

\textbf{Hit Die}: d10

\textbf{Skills}: Balance (Dex), Climb (Str), Handle Animal (Cha), Hide (Dex), Knowledge (all skills, taken individually) (Int), Listen (Wis), Move Silently (Dex), Profession (Wis), Ride (Dex), Search (Int), Speak Language (None), Spot (Wis), Survival (Wis), Swim (Str)

\textbf{Skills/Level}: 4 + Int modifier

\begin{center}
\begin{adjustwidth}{-4cm}{}
\begin{small}
\begin{tabular}{| c | c | c | c | c | c |}
\hline
LVL &BAB &F &R &W &Special \\
\hline
1 &1 &2 &2 &2 &Terrain Mastery \\
2 &2 &3 &3 &3 &Terrain Mastery \\
3 &3 &3 &3 &3 &Terrain Mastery \\
4 &4 &4 &4 &4 &Terrain Mastery, Planar Attunement \\
5 &5 &4 &4 &4 &Terrain Mastery, Horizon Step \\
6 &6/1 &5 &5 &5 &Terrain Mastery, Horizon Guide \\
\hline
\end{tabular}
\end{small}
\end{adjustwidth}
\end{center}

\textbf{Weapon and Armor Proficiency}: A horizon walker is proficient with all simple and martial weapons. Horizon walkers are proficient with light armor, medium armor, and shields (except tower shields).

\textbf{Terrain Mastery}: At each level, the Horizon Walker adds a new terrain environment to their repertoire from those given below. Terrain mastery gives a horizon walker a bonus on checks involving a skill useful in that terrain, or some other appropriate benefit. A horizon walker also knows how to fight dangerous creatures typically found in that terrain, gaining a +1 insight bonus on attack rolls and damage rolls against creatures with that terrain mentioned in the Environment entry of their descriptions. The horizon walker only gains the bonus if the creature description specifically lists the terrain type.

Horizon walkers take their terrain mastery with them wherever they go. They retain their terrain mastery bonuses on skill checks, attack rolls, and damage rolls whether they’re actually in the relevant terrain or not.

\textbf{Planar Attunement(Su)}: A 4th level horizon walker gains the ability to attune himself to a plane, gaining the benefits of terrain mastery for that plane. At 5th, and each level thereafter, he may select an additional plane to be simultaneously attuned to (up to 3 at 6th level).

A horizon walker can change the planes he is attuned to by spending a week in careful meditation. He must full rest each night, and spend 12 hours each day connecting to the planes he wishes to attune himself to. He may use the remaining hours of the day to engage in simple, non-strenuous activity. Combat or use of his horizon step ability will cause the attempt to fail, leaving him attuned to the same planes as he was before attempting to change.

\textbf{Horizon Step(Su)}: A 5th level horizon walker gains the ability to teleport a short distance every 1d4 rounds. Using this ability requires a swift action, the max range traveled is 60 feet, you must have line of sight to the desired destination, and if this ability would put you in a place that is already occupied by a solid body, it fails. This form of movement does not provoke attacks of opportunity, and is only available to a horizon walker wearing light, medium, or no armor.

The horizon walker may bring touched objects, so long as their weight does not exceed his maximum load. He cannot however bring other creatures.

\textbf{Horizon Guide(Su)}: A 6th level horizon walker may expend a standard action to allow himself and up to three allies within 60 feet to teleport a short distance. This teleportation functions like horizon step. This ability is usable up to three times per day, using it does not provoke attacks of opportunity.

\textbf{\large{Terrain Mastery Benefits}}

\textbf{Aquatic}: You gain a swim speed equal to half your land speed, or a +10-foot bonus to your swim speed if you have one. You gain a +1 insight bonus on attack and damage rolls against aquatic creatures.

\textbf{Desert}: You resist effects that tire you. You are immune to fatigue, and anything that would cause you to become exhausted makes you fatigued instead. You gain a +1 insight bonus on attack and damage rolls against desert creatures.

\textbf{Forest}: You have a +4 competence bonus on Hide checks. You gain a +1 insight bonus on attack and damage rolls against forest creatures.

\textbf{Hills}: You gain a +4 competence bonus on Listen checks. You gain a +1 insight bonus on attack and damage rolls against hills creatures.

\textbf{Marsh}: You have a +4 competence bonus on Move Silently checks. You gain a +1 insight bonus on attack and damage rolls against marsh creatures.

\textbf{Mountains}:  You gain tremorsense with a 30-foot range. You gain a +1 insight bonus on attack and damage rolls against mountain creatures.

\textbf{Plains}: You have a +4 competence bonus on Spot checks. You gain a +1 insight bonus on attack and damage rolls against plains creatures.

\textbf{Underground}: You have 60-foot darkvision, or 120-foot darkvision if you already had darkvision from another source. You gain a +1 insight bonus on attack and damage rolls against underground creatures.

\textbf{Astral (Planar)}: You gain telepathy with a range of 100 feet, and the spell-like ability to use detect thoughts at will. You gain a +1 insight bonus on attack and damage rolls against creatures native to the Astral Plane.

\textbf{Air (Planar)}: This kind of planar terrain mastery provides you with limited flight. Once per day you may gain a flight speed equal to your base land speed or 20 feet, whichever is less. This flight lasts for a number of rounds equal to your class level, activating this ability is a free action. Additionally you gain a +1 insight on attack and damage rolls against creatures native to the Elemental Plane of Air.

\textbf{Fiery (Planar)}: This kind of planar terrain mastery provides you with resistance to fire 10. You gain a +1 insight bonus on attack and damage rolls against outsiders and elementals with the fire subtype.

\textbf{Cold (Planar)}: This kind of planar terrain mastery provides you with resistance to cold 10. You gain a +1 insight bonus on attack and damage rolls against outsiders and elementals with the cold subtype.

\textbf{Negative (Planar)}: You gain the ability to rebuke or command undead as an evil cleric of your class level.

\textbf{Positive (Planar)}: Your connection with this plane sustains you. You no longer require food or drink to survive, and gain the ability Greater Improved Healing, letting you regain 1 hit point for every 60 minutes spent out of combat.

\textbf{Shadow (Planar)}: You gain the supernatural ability Hide in Plain Sight. You gain a +1 insight bonus on attack and damage rolls against creatures native to the Plane of Shadow.

\textbf{Cavernous (Planar)}: You gain a 10 foot climb speed, or a +10-foot bonus to your climb speed if you have one.

\textbf{Other (Planar)}: If other planes are in use additional Planar Terrains can be created.