\textbf{\huge{Jester}}

\textbf{Hit Die}: d6

\textbf{Skills}: Balance (Dex), Bluff (Cha), Climb (Str), Concentration (Con), Craft (Int), Diplomacy (Cha), Disable Device (Int), Disguise (Cha), Escape Artist (Dex), Gather Information (Cha), Hide (Dex), Intimidate (Cha), Jump (Str), Listen (Wis), Move Silently (Dex), Perform (Cha), Profession (Wis), Search (Int), Sense Motive (Wis), Sleight of Hand (Dex), Spellcraft (Int), Spot (Wis), Swim (Str), Tumble (Dex), Use Magic Device (Cha)

\textbf{Skills/Level}: 6 + Int modifier

\begin{center}
\begin{adjustwidth}{-4cm}{}
\begin{small}
\begin{tabular}{| c | c | c | c | c | c | c | c | c |}
\hline
LVL &BAB &F &R &W &Special &0 &1 &2 \\
\hline
1 &0 &0 &2 &0 &Harlequin's Mask, Ignore Components, Poison Use &2 &- &- \\
2 &1 &0 &3 &0 &Evasion, Laugh it Off &3 &0 &- \\
3 &2 &1 &3 &1 &Sneak Attack +1d6 &3 &1 &- \\
4 &3 &1 &4 &1 &Jester's Feint &3 &2 &0 \\
5 &3 &1 &4 &1 &Killer Clown, Last Trick &3 &3 &1 \\
6 &4 &2 &5 &2 &Sneak Attack +2d6, Pratfall &3 &3 &2 \\
\hline
\end{tabular}
\end{small}
\end{adjustwidth}
\end{center}

\textbf{Weapon and Armor Proficiency}: Jesters are proficient with light armor but not with shields of any kind. A Jester is proficient with no weapons, but suffers no attack penalty for using a weapon with which they are not proficient or which is made for a character of a different size than themselves. Even, perhaps especially, improvised weapons may be used without the usual -4 penalty.

\textbf{Spellcasting}: Jester is an Arcane caster with the same spells per day progression as a Bard. A Jester casts from the Jester Spell List (below). A Jester automatically knows every spell on his spell list. He can cast any spell he knows without preparing them ahead of time, provided that spell slots of an appropriate level are still available. To cast a Jester spell, he must have a Charisma of at least 10+spell level. The DC of the Jester’s spells is Charisma based, and the bonus spells are Charisma based.

\textbf{Harlequin's Mask}: As long as a Jester’s face is painted, masked, or adorned in the manner of a harlequin or other comedic figure, he is immune to compulsion effects.

\textbf{Ignore Components}: A Jester may cast spells from the Jester list without using any material components. This has no effect on any spells a Jester casts from other spell lists.

\textbf{Poison Use}: A Jester may prepare, apply, and use poison without any chance of poisoning himself.

\textbf{Evasion}: A jester can avoid even magical and unusal attacks with great agility. If she makes a successful Reflex saving throw against an attack that normally deals half damage on a successful save, she instead takes no damage. Evasion can be used only if the rogue is wearing light armor or no armor. A helpless rogue does not gain the benefits of evasion.

\textbf{Laugh it Off}: A Jester may add his Charisma modifier as a morale bonus to his saves.

\textbf{Sneak Attack}: If a jester can catch an opponent when he is unable to defend himself effectively from her attack, she can strike a vital spot for extra damage. 

The jester's attack deals extra damage any time her target would be denied a Dexterity bonus to AC (whether the target actually has a Dexterity bonus or not), or when the jester flanks her target. Should the jester score a critical hit with a sneak atack, this extra damage is not multiplied. 

\textbf{Jester's Feint}: As a swift action a Jester may toss a brightly colored object in the square of an enemy with a Sleight of Hand check opposed by the enemy’s Spot check. If he succeeds, the enemy is denied his Dex bonus for the Jester’s next attack. This ability has a range of 30 ft.

An enemy targeted by this ability multiple times gains a +5 bonus to Spot for each prior time he has been targeted, regardless of who won the prior checks. This bonus lasts for 24 hours.

\textbf{Killer Clown}: So long as he meets the requirements of the Harlequin’s Face ability, the Jester can make a special Intimidate check as a move action. If successful, this check causes the enemy to suffer the panicked condition for a round per Jester level. This is a mind-affecting fear effect. A creature targeted by this effect cannot be affected by it again until 24 hours have elapsed.

\textbf{Last Trick}: Anytime a Jester is killed or knocked unconscious, he may cast one of his spells known as if it were the spell in a contingency effect.

\textbf{Pratfall}: Any time a 6th level Jester strikes an opponent with a melee sneak attack, they may make a free trip attempt which does not provoke an attack of opportunity. They may use their Dexterity modifier as opposed to their Strength modifier for the purpose of this attempt.

\textbf{\large{Jester Spells}}

\begin{center}
\begin{adjustwidth}{-4cm}{}
\begin{small}
\begin{tabular}{| l | l |}
\hline
Level &Spells Known \\
\hline
**0** &\makecell{Alarm, Detect Magic, Detect Poison,\\ Grease, Unseen Servant, Ventriloquism} \\
**1** &\makecell{Fire Trap, Hideous Laughter, Magic Mouth,\\ Misdirection, Pyrotechnics, Reduce Person} \\
**2** &\makecell{Baleful Transposition, Explosive Runes,\\ Glitterdust, Invisibility, Rage, Touch of Idiocy} \\
\hline
\end{tabular}
\end{small}
\end{adjustwidth}
\end{center}
