\textbf{\huge{Soldier}}

\textbf{Hit Die}: d10

\textbf{Skills}: Balance (Dex), Climb (Str), Craft (Int), Escape Artist (Dex), Handle Animal (Cha), Heal (Wis), Jump (Str), Knowledge (all skills, taken individually) (Int), Listen (Wis), Move Silently (Dex), Profession (Wis), Ride (Dex), Spot (Wis), Survival (Wis), Swim (Str), Tumble (Dex), Use Rope (Dex)

\textbf{Skills/Level}: 6 + Int modifier

\begin{center}
\begin{adjustwidth}{-4cm}{}
\begin{small}
\begin{tabular}{| c | c | c | c | c | c |}
\hline
LVL &BAB &F &R &W &Special \\
\hline
1 &1 &2 &0 &2 &Combat Focus \\
2 &2 &3 &0 &3 &Active Assault, Problem Solver \\
3 &3 &3 &1 &3 &Pack Mule \\
4 &4 &4 &1 &4 &Bonus Feat, Weapon Training \\
5 &5 &4 &1 &4 &Improved Delay \\
6 &6/1 &5 &2 &5 &Bonus Feat, Array of Stunts, Foil Action \\
\hline
\end{tabular}
\end{small}
\end{adjustwidth}
\end{center}

\textbf{Weapon and Armor Proficiency}: A soldier is proficient with all simple and martial weapons and with all armor (heavy, medium, and light) and shields (including tower shields).

\textbf{Bonus Feat}: At 4th and 6th level a soldier gains a bonus feat in addition to any feats from their normal level progression.

\textbf{Combat Focus(Ex)}: If the soldier is in a situation that is stressful and/or dangerous enough that he would normally be unable to take 10 on skill checks, he may spend a swift action to gain combat focus. A soldier may end his combat focus at any time to reroll any die roll he makes, and if not used it ends on its own after a number of rounds equal to his class level. After voluntarily ending combat focus he must wait one round before re-entering it.

\textbf{Active Assault(Ex)}: A 2nd level soldier gains the ability to take a 5 foot step each turn as an immediate action, this is in addition to all other forms of movement (including the normal 5 foot step).

\textbf{Problem Solver(Ex)}: A 2nd level soldier may expend a swift action and gain the benefits of any [Combat] feat for which he meets the prerequisites and use it for a number of rounds equal to his class level. This ability may be used once per hour.

\textbf{Pack Mule(Ex)}: A 3rd level soldier suffers no penalties for carrying a medium load, and may retrieve stored items from his person without provoking an attack of opportunity.

\textbf{Weapon Training(Ex)}: A 4th level soldier gains the ability to become proficient with any weapon he spends a full day training with. He may take no other actions during this day, and if he is interrupted he loses all progress and must begin again.

\textbf{Improved Delay(Ex)}: A 5th level soldier may delay his actions in one round without compromising his initiative in the next round. In addition, a soldier may interrupt another action with his delayed action like it was a readied action (though he does not have to announce his intentions beforehand).

\textbf{Array of Stunts(Ex)}: A 6th level soldier may use an immediate action without sacrificing his swift action on his next turn.

\textbf{Foil Action(Ex)}: A 6th level soldier may use an immediate action to make a touch attack or ranged touch attack on any opponent within 30 ft. If this attack succeeds the opponent's action is wasted, and any spell slots, limited ability uses, potions, or the like used to power it are expended.

The only actions exempt from this ability are attack actions (standard or full round) and movement actions (standard, full round, or 5-foot step).