\textbf{\huge{Thief Acrobat}}

\textbf{Hit Die}: d6

\textbf{Skills}: Appraise (Int), Bluff (Cha), Balance (Dex), Climb (Str), Craft (Int), Disable Device (Int), Escape Artist (Dex), Hide (Dex), Intimidate (Cha), Jump (Str), Listen (Wis), Move Silently (Dex), Perform (Cha), Profession (Wis), Search (Int), Sense Motive (Wis), Sleight of Hand (Dex), Spot (Wis), Swim (Str), Tumble (Dex), Use Magic Device (Cha), Use Rope (Dex)

\textbf{Skills/Level}: 6 + Int modifier

\begin{center}
\begin{adjustwidth}{-4cm}{}
\begin{small}
\begin{tabular}{| c | c | c | c | c | c |}
\hline
LVL &BAB &F &R &W &Special \\
\hline
1 &0 &0 &2 &0 &Acrobatic Flair, Trapfinding, Pole Jump \\
2 &1 &0 &3 &0 &Sneak Attack +1d6, Evasion \\
3 &2 &1 &3 &1 &Sure Climb, Kip Up \\
4 &3 &1 &4 &1 &Detect Magic, Grapple Line, Skill Mastery \\
5 &3 &1 &4 &1 &Sneak Attack +2d6, Rapid Stealth, Improved Evasion \\
6 &4 &2 &5 &2 &Mercurial Charge, Athletic Cascade, Unsettling Choreography \\
\hline
\end{tabular}
\end{small}
\end{adjustwidth}
\end{center}

\textbf{Acrobatic Flair}: A Thief Acrobat may move her full movement while using the Tumble or Balance skill without suffering a penalty or increasing the DC of her check.

\textbf{Weapon and Armor Proficiency}: Thief Acrobats are proficient with all simple weapons, as well as the sap, the shortsword, the whip, the bolas, the long staff, and the shuriken. Thief Acrobats are proficient with light armor but not with shields of any kind.

\textbf{Pole Jump}: If holding a pole, spear, staff, long staff, or other pole-like object in both hands, a Thief Acrobat can add twice her reach to her final distance moved during a Jump check, and in this instance her jump distances are not limited by her height.

\textbf{Sure Climb}: A Thief Acrobat gains a climb speed equal to half her movement speed.

\textbf{Kip Up}: A Thief Acrobat may stand up from prone as a free action which does not provoke an attack of opportunity.

\textbf{Detect Magic(Sp)}: A Thief Acrobat may use detect magic at-will as a spell-like ability. A Thief Acrobat may use her Appraise Skill in place of her Spellcraft in order to glean additional information from her detect magic.

\textbf{Grapple Line}: A Thief Acrobat may fire a missile weapon designed as a grappling weapon at an unoccupied square and, if it does at least 1 point of damage to an object filling that square (wall, ceiling, statue, etc) or a securely affixed object (ceiling post, small statue, etc) the Thief acrobat may run a rope from his current position to that location as a full round action. He may then use this rope to make a Balance or Climb check as normal.

\textbf{Skill Mastery}: A Thief Acrobat is able to take 10 on any Appraise, Balance, Disable Device, Jump, Hide, Move Silently, and Tumble checks. 

\textbf{Rapid Stealth}: A Thief acrobat does not suffer the -10 penalty to Move Silently or Hide for moving at her full normal speed.

\textbf{Mercurial Charge}: As a full round action, a thief acrobat may move up to twice her movement speed and then make a single attack at her full Base Attack Bonus. The thief acrobat may not move back on herself while using this form of movement, if she moves at least 10 feet before making her attack she adds +2 to her roll and -2 to her AC for the next turn. Tumble checks taken during this action suffer a penalty of -10.

\textbf{Athletic Cascade}: If a Thief acrobat moves before making an attack, for the purpose of flanking she may count any square she has moved through as threatening an opponent, in addition to the space she is actually attacking from. In this manner she may even flank with herself.

\textbf{Unsettling Choreography}: A thief acrobat of 6th level may use her Dexterity modifier in place of her Strength modifier when making trip or bullrush attempts.