\textbf{\huge{Slayer}}

\textbf{Hit Die}: d8

\textbf{\large{Requirements}}

To qualify to become a slayer, a character must fulfill one of the following criteria.

\textbf{Base Attack Bonus}: +4

\textbf{Skills}: Concentration 7 ranks

\textbf{Skills}: Bluff (Cha), Concentration (Con), Knowledge (dungeoneering) (Int), Listen (Wis), Psicraft (Int), Sense Motive (Wis), Spot (Wis), Survival (Wis)

\textbf{Skills/Level}: 4 + Int modifier

\begin{center}
\begin{adjustwidth}{-4cm}{}
\begin{small}
\begin{tabular}{| c | c | c | c | c | c |}
\hline
LVL &BAB &F &R &W &Special \\
\hline
1 &1 &0 &2 &2 &\makecell{Brain nausea, combat style, enemy\\ sense, favored enemy, lucid buffer} \\
2 &2 &0 &3 &3 &Blast feedback \\
\hline
\end{tabular}
\end{small}
\end{adjustwidth}
\end{center}

\textbf{Weapon and Armor Proficiency}: Slayers are proficient with all simple and martial weapons and with all types of armor.

\textbf{Brain Nausea}:

\textbf{Combat Style}: At 1st level, a slayer must select one of two combat styles to pursue, psionics or psionic defense. 

If the slayer selects psionics, then each slayer level gained grants additional power points per day and access to new powers as if he had also gained a level in a manifesting class he belonged to before adding the prestige class.

If the slayer selects psionic defense, at 2nd level he gains an immunity to all mind-affecting devices, powers, and spells. 

\textbf{Enemy Sense}: A slayer can sense the presence of her favored enemy within 60 feet of herself, even if they are hidden by darkness or walls, but she cannot discern their exact location.

\textbf{Favored Enemy}: When she enters the class, a slayer formally declares a type of psionic creature as the enemy she detests above all others. Due to her extensive study of her foes and training in the proper techniques for combating them, she gains a +2 bonus on Bluff, Listen, Sense Motive, Spot, and Survival checks when using these skills against her favored enemy.

Likewise, she gets a +2 bonus on weapon damage rolls, and a +1 enhancement to critical range against creatures of this kind.

\textbf{Lucid Buffer}: A slayer becomes especially skilled at resisting mental attacks. She gains a +4 competence bonus on saving throws against all compulsions and mind-affecting effects. This ability is active even if the slayer is unconscious, stunned, or otherwise helpless.

\textbf{Blast Feedback}: At 2nd level, if a slayer makes her saving throw when attacked with mind blast, the mind blast rebounds upon the attacker. Only the original attacker is targeted in the rebound effect. If the original attacker fails a Will saving throw (DC equal to that of the original attack), the attacker is affected normally by the mind blast.